### 2022-05-27 tex/ill.tex
[ more ] thesis writing

@@

In LJ, two distinct, but equiderivable, canonical definitions of $\wedge$ can
be given.

In the first approach, $\wedge^-$ is conceived to be a
\emph{categorial product}.
Such a product is constructed by providing two maps in from the same antecedents
$\Gamma$.
It is used by projecting out one of the sides.

\begin{mathpar}
  \inferrule*[right=$\wedge^-$-r]
  {\Gamma \vdash A \\ \Gamma \vdash B}
  {\Gamma \vdash A \wedge^- B}

@@

  \inferrule*[right=$\wedge^-$-l$_0$]
  {\Gamma, A \vdash C}
  {\Gamma, A \wedge^- B \vdash C}

@@

  \inferrule*[right=$\wedge^-$-l$_1$]
  {\Gamma, B \vdash C}
  {\Gamma, A \wedge^- B \vdash C}
\end{mathpar}

In the second approach, $\wedge^+$ is conceived to be a \emph{tensor product}.
Intuitively, $\wedge^+$ internalises the comma of context concatenation.
Such a product is used by giving access to both sides simultaneously.
It is constructed by constructing both sides and combining the antecedents
required by each side.

\begin{mathpar}
  \inferrule*[right=$\wedge^+$-r]
  {\Gamma \vdash A \\ \Delta \vdash B}
  {\Gamma, \Delta \vdash A \wedge^+ B}

@@

  \inferrule*[right=$\wedge^+$-l]
  {\Gamma, A, B \vdash C}
  {\Gamma, A \wedge^+ B \vdash C}
\end{mathpar}

When we prove the logical equivalence of these two formulations, we notice that
the structural rules of weakening and contraction are essential.
When we remove weakening and contraction, $\wedge^-$ and $\wedge^+$ become
logically distinct connectives, which we notate $\&$ and $\otimes$,
respectively.

\begin{mathpar}
  \inferrule*[right=$\wedge^-$-r]
  {%
    \inferrule*[right=Weak$^*$,fraction={\cdot\cdots\cdot}]
    {\Gamma \vdash A}
    {\Gamma, \Delta \vdash A}
    \\
    \inferrule*[Right=Weak$^*$,fraction={\cdot\cdots\cdot}]
    {\Delta \vdash B}
    {\Gamma, \Delta \vdash B}
  }
  {\Gamma, \Delta \vdash A \wedge^- B}

  \inferrule*[right=Contr]
  {%
    \inferrule*[Right=$\wedge^-$-l$_0$]
    {%
      \inferrule*[Right=$\wedge^-$-l$_1$]
      {\Gamma, A, B \vdash C}
      {\Gamma, A, A \wedge^- B \vdash C}
    }
    {\Gamma, A \wedge^- B, A \wedge^- B \vdash C}
  }
  {\Gamma, A \wedge^- B \vdash C}
\end{mathpar}

\begin{mathpar}
  \inferrule*[right=Contr$^*$,fraction={\cdot\cdots\cdot}]
  {%
    \mprset{defaultfraction}
    \inferrule*[Right=$\wedge^+$-r]
    {\Gamma \vdash A \\ \Gamma \vdash B}
    {\Gamma, \Gamma \vdash A \wedge^+ B}
  }
  {\Gamma \vdash A \wedge^+ B}

  \inferrule*[right=$\wedge^+$-l]
  {%
    \inferrule*[Right=Weak]
    {\Gamma, A \vdash C}
    {\Gamma, A, B \vdash C}
  }
  {\Gamma, A \wedge^+ B \vdash C}

  \inferrule*[right=$\wedge^+$-l]
  {%
    \inferrule*[Right=Weak]
    {\Gamma, B \vdash C}
    {\Gamma, A, B \vdash C}
  }
  {\Gamma, A \wedge^+ B \vdash C}
\end{mathpar}

\begin{mathpar}
  \inferrule*[right=Promotion]
  {\oc\Gamma \vdash A}
  {\oc\Gamma \vdash \oc A}

  \inferrule*[right=Dereliction]
  {\Gamma, A \vdash B}
  {\Gamma, \oc A \vdash B}

  \inferrule*[right=Weakening]
  {\Gamma \vdash B}
  {\Gamma, \oc A \vdash B}

  \inferrule*[right=Contraction]
  {\Gamma, \oc A, \oc A \vdash B}
  {\Gamma, \oc A \vdash B}
\end{mathpar}

@@

\begin{mathpar}
  \inferrule*[right=$\otimes$-l]
  {%
    \inferrule*[Right=$\otimes$-r]
    {%
      \inferrule*[right=Id]{ }{P \vdash P} \\
      \inferrule*[Right=Id]{ }{Q \vdash Q}
    }
    {P, Q \vdash P \otimes Q}
  }
  {P \otimes Q \vdash P \otimes Q}

@@

  \inferrule*[right=Pro]
  {%
    \inferrule*[Right=Der]
    {%
      \inferrule*[Right=Id]{ }{P \vdash P}
    }
    {\oc P \vdash P}
  }
  {\oc P \vdash \oc P}
\end{mathpar}

>>>>

Linear logic is a good starting point for our investigations into usage
restrictions because it is well known, well understood, and exhibits most of the
difficulties we will come across.
Linear logic's lack of general weakening and contraction will be a typical
feature of the calculi we will see, and the exponential modality $\oc$ (bang)
will be the prototype for a range of modalities I will consider.

@@

%In LJ, two distinct, but equiderivable, canonical definitions of $\wedge$ can
%be given.
%
%In the first approach, $\wedge^-$ is conceived to be a
%\emph{categorial product}.
%Such a product is constructed by providing two maps in from the same antecedents
%$\Gamma$.
%It is used by projecting out one of the sides.
%
%\begin{mathpar}
%  \inferrule*[right=$\wedge^-$-r]
%  {\Gamma \vdash A \\ \Gamma \vdash B}
%  {\Gamma \vdash A \wedge^- B}
%
%  \and
%
%  \inferrule*[right=$\wedge^-$-l$_0$]
%  {\Gamma, A \vdash C}
%  {\Gamma, A \wedge^- B \vdash C}
%
%  \and
%
%  \inferrule*[right=$\wedge^-$-l$_1$]
%  {\Gamma, B \vdash C}
%  {\Gamma, A \wedge^- B \vdash C}
%\end{mathpar}
%
%In the second approach, $\wedge^+$ is conceived to be a \emph{tensor product}.
%Intuitively, $\wedge^+$ internalises the comma of context concatenation.
%Such a product is used by giving access to both sides simultaneously.
%It is constructed by constructing both sides and combining the antecedents
%required by each side.
%
%\begin{mathpar}
%  \inferrule*[right=$\wedge^+$-r]
%  {\Gamma \vdash A \\ \Delta \vdash B}
%  {\Gamma, \Delta \vdash A \wedge^+ B}
%
%  \and
%
%  \inferrule*[right=$\wedge^+$-l]
%  {\Gamma, A, B \vdash C}
%  {\Gamma, A \wedge^+ B \vdash C}
%\end{mathpar}
%
%When we prove the logical equivalence of these two formulations, we notice that
%the structural rules of weakening and contraction are essential.
%When we remove weakening and contraction, $\wedge^-$ and $\wedge^+$ become
%logically distinct connectives, which we notate $\&$ and $\otimes$,
%respectively.
%
%\begin{mathpar}
%  \inferrule*[right=$\wedge^-$-r]
%  {%
%    \inferrule*[right=Weak$^*$,fraction={\cdot\cdots\cdot}]
%    {\Gamma \vdash A}
%    {\Gamma, \Delta \vdash A}
%    \\
%    \inferrule*[Right=Weak$^*$,fraction={\cdot\cdots\cdot}]
%    {\Delta \vdash B}
%    {\Gamma, \Delta \vdash B}
%  }
%  {\Gamma, \Delta \vdash A \wedge^- B}
%
%  \and
%
%  \inferrule*[right=Contr]
%  {%
%    \inferrule*[Right=$\wedge^-$-l$_0$]
%    {%
%      \inferrule*[Right=$\wedge^-$-l$_1$]
%      {\Gamma, A, B \vdash C}
%      {\Gamma, A, A \wedge^- B \vdash C}
%    }
%    {\Gamma, A \wedge^- B, A \wedge^- B \vdash C}
%  }
%  {\Gamma, A \wedge^- B \vdash C}
%\end{mathpar}
%
%\begin{mathpar}
%  \inferrule*[right=Contr$^*$,fraction={\cdot\cdots\cdot}]
%  {%
%    \mprset{defaultfraction}
%    \inferrule*[Right=$\wedge^+$-r]
%    {\Gamma \vdash A \\ \Gamma \vdash B}
%    {\Gamma, \Gamma \vdash A \wedge^+ B}
%  }
%  {\Gamma \vdash A \wedge^+ B}
%
%  \and
%
%  \inferrule*[right=$\wedge^+$-l]
%  {%
%    \inferrule*[Right=Weak]
%    {\Gamma, A \vdash C}
%    {\Gamma, A, B \vdash C}
%  }
%  {\Gamma, A \wedge^+ B \vdash C}
%
%  \and
%
%  \inferrule*[right=$\wedge^+$-l]
%  {%
%    \inferrule*[Right=Weak]
%    {\Gamma, B \vdash C}
%    {\Gamma, A, B \vdash C}
%  }
%  {\Gamma, A \wedge^+ B \vdash C}
%\end{mathpar}

\begin{mathpar}
  \ebrule{%
    \hypo{\oc\Gamma \vdash A}
    \infer1[Promotion]{\oc\Gamma \vdash \oc A}
  }

@@

  \ebrule{%
    \hypo{\Gamma, A \vdash B}
    \infer1[Dereliction]{\Gamma, \oc A \vdash B}
  }

@@

  \ebrule{%
    \hypo{\Gamma \vdash B}
    \infer1[Weakening]{\Gamma, \oc A \vdash B}
  }

@@

  \ebrule{%
    \hypo{\Gamma, \oc A, \oc A \vdash B}
    \infer1[Contraction]{\Gamma, \oc A \vdash B}
  }
\end{mathpar}

@@

\begin{mathpar}
  \ebrule{%
    \infer0[Id]{P \vdash P}
    \infer0[Id]{Q \vdash Q}
    \infer2[$\otimes$-r]{P, Q \vdash P \otimes Q}
    \infer1[$\otimes$-l]{P \otimes Q \vdash P \otimes Q}
  }

@@

  \ebrule{%
    \infer0[Id]{P \vdash P}
    \infer1[Der]{\oc P \vdash P}
    \infer1[Pro]{\oc P \vdash \oc P}
  }
\end{mathpar}

### 2022-05-27 tex/lnl.tex
[ writing ] lots
[ more ] state the other LnL translation lemma
[ more ] thesis writing

In L/nL, we have a \emph{linear} and an \emph{intuitionistic} mode, with
separate types (respectively $A$ and $X$) and typing judgements (respectively
$\vdash_{\mathcal L}$ and $\vdash_{\mathcal C}$) connected by modalities $F$ and
$G$.
The mode of the conclusion type is the same as the mode of the judgement, so
only a distinction in the conclusion mode is necessary.
To achieve this distinction in the types, we have an indexed type family
$\mathrm{Ty} : \mathrm{Frag} \to \mathrm{Set}$, and set the framework types to
be the type $(f : \mathrm{Frag}) \times \mathrm{Ty}\,f$.
% \AgdaDatatype{Ty}\AgdaSymbol{:}\AgdaDatatype{Frag}\AgdaSymbol{$\to$}
% \AgdaDatatype{Set}

In L/nL, while linear judgements can have both linear and intuitionistic
assumptions, intuitionistic judgements can only have intuitionistic assumptions.
We encode this invariant on intuitionistic judgements using the $\Box$
premise combinator on all intuitionistic conclusions and wherever
intuitionistic premises occur for linear conclusions.

@@

The translations largely follow Benton's originals.

>>>>

In L/nL, we have a \emph{linear} and an \emph{intuitionistic} mode, with
separate types (respectively $A$ and $X$) and typing judgements (respectively
$\vdash_{\mathcal L}$ and $\vdash_{\mathcal C}$) connected by modalities $F$ and
$G$.
The mode of the conclusion type is the same as the mode of the judgement, so
only a distinction in the conclusion mode is necessary.
To achieve this distinction in the types, I have an indexed type family
$\mathrm{Ty} : \mathrm{Frag} \to \mathrm{Set}$, and set the framework types to
be the type $(f : \mathrm{Frag}) \times \mathrm{Ty}\,f$.
% \AgdaDatatype{Ty}\AgdaSymbol{:}\AgdaDatatype{Frag}\AgdaSymbol{$\to$}
% \AgdaDatatype{Set}
I present these judgements in a standard paper style in \cref{fig:lnl-types}.

In L/nL, while linear judgements can have both linear and intuitionistic
assumptions, intuitionistic judgements can only have intuitionistic assumptions.
I encode this invariant on intuitionistic judgements using the $\Box$
premise combinator on all intuitionistic conclusions and wherever
intuitionistic premises occur for linear conclusions, as seen in
\cref{fig:lnl-desc}.
This scheme means that the rules contain the maximal number of boxes, which is
convenient when consuming terms.
For ease of \emph{producing} terms, we would want a ``garbage in; garbage out''
style with a minimal number of boxes, which could be achieved in two different
ways:
\begin{itemize}
  \item Ensure that $\Gamma, \gr1\,\lin A \vdash \intu X$ is never derivable.
    This leaves boxes only on rules $1$-I and $G$-I.
  \item Ensure that, when working bottom-up, we never transition from a linear
    to an intuitionistic conclusion with linear assumptions present.
    This leaves boxes only on rules $F$-I and $G$-E.
\end{itemize}
It would be interesting to show the equivalence of these three approaches, but
that is left to future work.

\begin{figure}
  \begin{align*}
    A, B, C &\Coloneqq I \mid A \otimes B \mid A \multimap B \mid FX \\
    X, Y, Z &\Coloneqq 1 \mid X \times Y \mid X \to Y \mid GA \\
    \mathcal J &\Coloneqq \lin A \mid \intu X
  \end{align*}
  \caption{Types and judgement forms of L/nL}
  \label{fig:lnl-types}
\end{figure}

\begin{figure}
  \begin{mathpar}
    % lin rules
    \ebrule[comb]{%
      \hypo{I^*}
      \infer1[$I$-I]{\vdash \lin I}
    }
    \and
    \ebrule[comb]{%
      \hypo{\vdash \lin I}
      \hypo{*}
      \hypo{\vdash \lin C}
      \infer3[$I$-E]{\vdash \lin C}
    }
    \and
    \ebrule[comb]{%
      \hypo{\vdash \lin A}
      \hypo{*}
      \hypo{\vdash \lin B}
      \infer3[$\otimes$-I]{\vdash \lin A \otimes B}
    }
    \and
    \ebrule[comb]{%
      \hypo{\vdash \lin A \otimes B}
      \hypo{*}
      \hypo{\gr1\,\lin A, \gr1\,\lin B \vdash \lin C}
      \infer3[$\otimes$-E]{\vdash \lin C}
    }
    \and
    \ebrule[comb]{%
      \hypo{\gr1\,\lin A \vdash \lin B}
      \infer1[$\multimap$-I]{\vdash \lin A \multimap B}
    }
    \and
    \ebrule[comb]{%
      \hypo{\vdash \lin A \multimap B}
      \hypo{*}
      \hypo{\vdash \lin A}
      \infer3[$\multimap$-E]{\vdash \lin B}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box\plr{\vdash \intu X}}
      \infer1[$F$-I]{\vdash \lin FX}
    }
    \and
    \ebrule[comb]{%
      \hypo{\vdash \lin FX}
      \hypo{*}
      \hypo{\gr\omega\,\intu X \vdash \lin C}
      \infer3[$F$-E]{\vdash \lin C}
    }
    \and
    % int rules
    \ebrule[comb]{%
      \hypo{\Box\plr{\dot1}}
      \infer1[$1$-I]{\vdash \intu 1}
    }
    \and
    \text{(no $1$-E)}
    \and
    \ebrule[comb]{%
      \hypo{\Box(\vdash \intu X}
      \hypo{\dottimes}
      \hypo{\vdash \intu Y)}
      \infer3[$\times$-I]{\vdash \intu X \times Y}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box\plr{\vdash \intu X \times Y}}
      \infer1[$\times$-El]{\vdash \intu X}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box\plr{\vdash \intu X \times Y}}
      \infer1[$\times$-Er]{\vdash \intu Y}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box\plr{\gr\omega\,\intu A \vdash \intu B}}
      \infer1[$\to$-I]{\vdash \intu A \to B}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box(\vdash \intu A \to B}
      \hypo{\dottimes}
      \hypo{\vdash \intu A)}
      \infer3[$\to$-E]{\vdash \intu B}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box\plr{\vdash \lin A}}
      \infer1[$G$-I]{\vdash \intu GA}
    }
    \and
    \ebrule[comb]{%
      \hypo{\Box\plr{\vdash \intu GA}}
      \infer1[$G$-E]{\vdash \lin A}
    }
  \end{mathpar}
  \caption{Description of the logical rules of L/nL}
  \label{fig:lnl-desc}
\end{figure}

\begin{proposition}
  We can construct the following translations.
  \begin{align}
    (\Theta \vdash_{\mathcal C} X) &\to (\gr\omega\Theta \vdash \intu X) \\
    (\Theta; \Gamma \vdash_{\mathcal L} A) &\to
    (\gr\omega\Theta, \gr1\Gamma \vdash \lin A)
  \end{align}
\end{proposition}

\begin{proposition}
  We can construct the following translations, where $\Gamma_{\gr r}$ is the
  list of types in $\Gamma$ that are annotated $\gr r$.%
  \todo{I'm not sure the resultant contexts are well formed.}
  \begin{align}
    (\Gamma \vdash \intu X) &\to (\Gamma_{\gr\omega} \vdash_{\mathcal C} X) \\
    (\Gamma \vdash \lin A) &\to
    (\Gamma_{\gr\omega}; \Gamma_{\gr1} \vdash_{\mathcal L} A)
  \end{align}
\end{proposition}

@@

The translations largely follow Benton's originals.
In this section, I take $\name$ to be the system described in
\cref{fig:lr-bunched} instantiated to the $\{\gr0 > \gr\omega < \gr1\}$
posemiring and restricted to the fragment with only connectives $I$, $\otimes$,
$\multimap$, and $\oc\gr\omega$.
Notably, this excludes $\oc\gr0$ and $\oc\gr1$.
I write $\oc\gr\omega$ as just $\oc$, as in traditional linear logic.
Under these restrictions, Benton's translations of types can be used verbatim
(\cref{fig:lnl-lr-types}).

\begin{figure}
  \centering
  \begin{subfigure}{.49\linewidth}
    \centering
    \begin{align*}
      (-)^\circ : \mathrm{Ty}_{\name} \to \mathrm{Ty}_{\lin} \\
      \begin{aligned}
        I^\circ &= I \\
        \plr{A \otimes B}^\circ &= A^\circ \otimes B^\circ \\
        \plr{A \multimap B}^\circ &= A^\circ \multimap B^\circ \\
        \plr{\oc A}^\circ &= GFA^\circ
      \end{aligned}
    \end{align*}
  \end{subfigure}
  \begin{subfigure}{.49\linewidth}
    \centering
    \begin{align*}
      (-)^* : \mathrm{Ty}_\lnl \to \mathrm{Ty}_{\name} \\
      \begin{aligned}
        I^* &= I \\
        \plr{A \otimes B}^* &= A^* \otimes B^* \\
        \plr{A \multimap B}^* &= A^* \multimap B^* \\
        \plr{FX}^* &= \oc X^* \\
        1^* &= I \\
        \plr{X \times Y}^* &= \oc X^* \otimes \oc Y^* \\
        \plr{X \to Y}^* &= \oc X^* \multimap Y^* \\
        \plr{GA}^* &= A^*
      \end{aligned}
    \end{align*}
  \end{subfigure}
  \caption{Translation of types between L/nL and $\name$}
  \label{fig:lnl-lr-types}
\end{figure}

We extend both $(-)^\circ$ and $(-)^*$ to contexts pointwise on the types.
For $(-)^\circ$, this means that the translation lands outside what is usually
expressible in L/nL whenever the context contains annotation $\gr\omega$.
For example, $\plr{\gr\omega I}^\circ = \plr{\gr\omega\,\lin I}$, and we do not
see ``$\gr\omega\,\lin$'' in translations from Benton's L/nL.
This could be fixed by inserting $G$ in such cases.
As for $(-)^*$, note that we do not insert a $\oc$ on intuitionistic assumptions
as Benton does.
Instead, the annotation $\gr\omega$ achieves the same effect for us.
This discrepancy essentially amounts to the fact that $\name$ is more like DILL
than Girard's ILL, and Benton's translations act upon the latter.

\begin{theorem}
  We can translate from $\name$ to the linear fragment of L/nL.
  \begin{align}
    (\Gamma \vdash_{\name} A) \to (\Gamma^\circ \vdash_\lnl \lin A^\circ)
  \end{align}
\end{theorem}

\begin{theorem}
  We can translate any L/nL term to a $\name$ term as follows.
  \begin{align}
    (\Gamma \vdash_\lnl \intu X) &\to (\Gamma^* \vdash_{\name} X^*) \\
    (\Gamma \vdash_\lnl \lin A) &\to (\Gamma^* \vdash_{\name} A^*)
  \end{align}
\end{theorem}

### 2022-05-27 tex/lrkits.tex
[ more ] thesis writing

\begin{definition}[Simple recursive environment]\label{def:simple-rec-env}
  A \emph{recursive $\V$-environment} between simply typed contexts $\Gamma$ and
  $\Delta$ is defined by cases on the shape of $\Delta$ (where
  $\Gamma \env\V_R \Delta$ is the notation for the type of recursive
  environments for given $\V$, $\Gamma$, and $\Delta$):
  \begin{itemize}
    \item There is one environment $\alr{} : \Gamma \env\V {\cdot}$.
    \item For $\rho_l : \Gamma \env\V_R \Delta_l$ and
      $\rho_r : \Gamma \env\V \Delta_r$, we have an environment
      $\alr{\rho_l, \rho_r} : \Gamma \env\V_R \Delta_l, \Delta_r$.
    \item For any value $v : \V\,\Gamma\,A$, we have an environment
      $\alr{v} : \Gamma \env\V_R A$.
  \end{itemize}
\end{definition}

@@

\begin{definition}[Usage-annotated recursive environment]\label{def:lr-rec-env}
  A \emph{recursive $\V$-environment} between annotated contexts $\Gamma$ and
  $\Delta$ is defined by cases on the shape of $\Delta$ (where
  $\Gamma \env\V_R \Delta$ is the notation for the
  type of recursive environments for given $\V$, $\Gamma$, and $\Delta$):
  \begin{itemize}
    \item There is one environment $\alr{} : \grP\gamma \env\V {\cdot}$
      whenever $\grP \leq \gr0$.
    \item For $\rho_l : \grPl\gamma \env\V_R \Delta_l$ and
      $\rho_r : \grPr\gamma \env\V_R \Delta_r$, we have an environment
      $\alr{\rho_l, \rho_r} : \grP\gamma \env\V_R \Delta_l, \Delta_r$ whenever
      $\grP \leq \grPl + \grPr$.
    \item For any value $v : \V\,\grPprime\gamma\,A$, we have an environment
      $\alr{v} : \grP\gamma \env\V_R \gr rA$ whenever
      $\grP \leq \gr r\grPprime$.
  \end{itemize}
\end{definition}

>>>>

\begin{definition}[Simple recursive environment]\label{def:simple-rec-env}
  A \emph{recursive $\V$-environment} between simply typed contexts $\Gamma$ and
  $\Delta$ is defined by cases on the shape of $\Delta$ (where
  $\Gamma \env\V_R \Delta$ is the notation for the type of recursive
  environments for given $\V$, $\Gamma$, and $\Delta$):
  \begin{itemize}
    \item There is one environment $\alr{} : \Gamma \env\V_R {\cdot}$.
    \item For $\rho_l : \Gamma \env\V_R \Delta_l$ and
      $\rho_r : \Gamma \env\V_R \Delta_r$, we have an environment
      $\alr{\rho_l, \rho_r} : \Gamma \env\V_R \Delta_l, \Delta_r$.
    \item For any value $v : \V\,\Gamma\,A$, we have an environment
      $\alr{v} : \Gamma \env\V_R A$.
  \end{itemize}
\end{definition}

@@

\begin{definition}[Usage-annotated recursive environment]\label{def:lr-rec-env}
  A \emph{recursive $\V$-environment} between annotated contexts $\Gamma$ and
  $\Delta$ is defined by cases on the shape of $\Delta$ (where
  $\Gamma \env\V_R \Delta$ is the notation for the
  type of recursive environments for given $\V$, $\Gamma$, and $\Delta$):
  \begin{itemize}
    \item There is one environment $\alr{} : \grP\gamma \env\V_R {\cdot}$
      whenever $\grP \leq \gr0$.
    \item For $\rho_l : \grPl\gamma \env\V_R \Delta_l$ and
      $\rho_r : \grPr\gamma \env\V_R \Delta_r$, we have an environment
      $\alr{\rho_l, \rho_r} : \grP\gamma \env\V_R \Delta_l, \Delta_r$ whenever
      $\grP \leq \grPl + \grPr$.
    \item For any value $v : \V\,\grPprime\gamma\,A$, we have an environment
      $\alr{v} : \grP\gamma \env\V_R \gr rA$ whenever
      $\grP \leq \gr r\grPprime$.
  \end{itemize}
\end{definition}
